---
output: rmarkdown::github_document
---

# whatamesh

Tools to Work with ASCII MeSH Files

## Description

Tools to Work with ASCII MeSH Files

Ref:

- <ftp://nlmpubs.nlm.nih.gov/online/mesh/MESH_FILES/asciimesh/>
- <https://stackoverflow.com/questions/52814022/how-to-split-txt-file-at-specific-location-and-import-each-part-as-table-in-r/52815428?noredirect=1#comment92554994_52815428>

## What's Inside The Tin

The following functions are implemented:

- `list_mesh_files`:	List ASCII MeSH Files Available For Download
- `read_mesh_file`:	Download and parse an ASCII MeSH File

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/whatamesh")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(whatamesh)

# current verison
packageVersion("whatamesh")

```

### List Remote MeSH Files

```{r}
list_mesh_files()
```


### Read & Parse a MeSH File

If the string passed in matches a local filename it will be read in locally, otherwise it will be downloaded. NOTE: large files take a while.

Nested:

```{r}
read_mesh_file("q2018.bin")
```


Wide:

```{r}
read_mesh_file("q2018.bin", wide = TRUE)
```
